\TheTitle

### 2019-02-28 Paper1/introduction.tex
mini change introduction

Due to the randomness of the solution, one is interested in determining the expectation value or the variance, i.e.
\begin{align*}
\text{E}[\bm{u}] = \langle \bm{u} \rangle,\qquad \text{Var}[\bm{u}] = \langle \left( \bm{u}-\text{E}[\bm{u}]\right)^2\rangle,
\end{align*}
where we use the bracket operator $\langle \cdot \rangle := \int_{\Theta} \cdot \prod_{i=1}^s f_{\Xi,i}(\xi_i)d\xi_1 \cdots d\xi_s$. More generally, one is interested in determining the moments of the solution for a given set of basis functions $\varphi_{i}:\Theta\to\mathbb{R}$ such that for the multi-index $i = (i_1,\cdots,i_s)$ we have $|i| \leq M$. Commonly one chooses orthonormal polynomials as basis functions \cite{xiu2002wiener}, i.e. $\langle \varphi_n \varphi_m \rangle = \delta_{nm}$.  The moments are then given by $\bm{\hat u_i} := \langle \bm{u}\varphi_i \rangle$ can for example be used to span the solution \cite{wiener1938homogeneous}. \\

>>>>

Due to the randomness of the solution, one is interested in determining the expectation value or the variance, i.e.
\begin{align*}
\text{E}[\bm{u}] = \langle \bm{u} \rangle,\qquad \text{Var}[\bm{u}] = \langle \left( \bm{u}-\text{E}[\bm{u}]\right)^2\rangle,
\end{align*}
where we use the bracket operator $\langle \cdot \rangle := \int_{\Theta} \cdot \prod_{i=1}^s f_{\Xi,i}(\xi_i)d\xi_1 \cdots d\xi_s$. More generally, one is interested in determining the moments of the solution for a given set of basis functions $\varphi_{i}:\Theta\to\mathbb{R}$ such that for the multi-index $i = (i_1,\cdots,i_s)$ we have $|i| \leq M$. Commonly one chooses orthonormal polynomials as basis functions \cite{xiu2002wiener}, i.e. $\langle \varphi_n \varphi_m \rangle = \delta_{nm}$.  The moments are then given by $\bm{\hat u_i} := \langle \bm{u}\varphi_i \rangle$. Besides facilitating the computation of the expectation value and variance, the moments can be used to span the solution in $\bm\xi$ \cite{wiener1938homogeneous}. \\
